---
title: "p8105_hw1_su2145"
output: github_document
date: "2022-09-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW 1

#Load Libraries 
```{r}
library(tidyverse)


```
#Get Data 
```{r}
library(tidyverse)

data("penguins", package = "palmerpenguins")

nrow(penguins)
ncol(penguins)
head(penguins)

flipper_l <- penguins %>%
  pull(flipper_length_mm)
mean_flip <- mean(flipper_l, na.rm = TRUE) #ignores missing values in the mean calculation 

penguins %>%
ggplot(aes(x = flipper_length_mm, y = bill_length_mm, color = species)) + 
  geom_point() 

  ggsave("./plots/scatterplot.pdf")

```

Penguins Data - This data includes information on a sample of Penguins including Species, island, bill length, flipper length, body mass, sex, year. It includes 8 variables and 344 rows. 


The mean of the sample is `r mean_flip`

```{r}
samp = rnorm(10) 
length(samp)

example_df = tibble(
  vec_numeric = samp,
  vev_log = samp > 0,
  vec_char = c("My", "name", "is", "Sabah", "a", "b", "c", "d", "e", "f"),
  vec_factor = factor(c("male", "male", "male",  "female", "female", "other", "other", "other", "other", "other"))
)


example_df %>%
  pull(vec_numeric) %>%
  mean()

example_df %>%
  pull(vev_log) %>%
  mean() 

example_df %>%
  pull(vec_char) %>%
  mean() 

example_df %>%
  pull(vec_factor) %>%
  mean()


```
Cannot get the mean value of a character or factor. You can get the mean value of the numeric and logical vector 

Checking to see if as.numeric function works on variables 

``` {r echo=T, results='hide'}

example_df %>%
pull(vec_char) %>%
  as.numeric

example_df %>%
pull(vec_factor) %>%
  as.numeric()

example_df %>%
pull(vev_log) %>%
  as.numeric

```


